### 2018-05-20 2_wmm.tex
Add some comments to the paper.

The relation~$r\,\subseteq~\mathbb{E}~\times~\mathbb{E}$ is a set of pairs of events (a subset of Cartesian product of two sets of events). There are two kinds of relations between events: \textit{basic relations} that capture the semantics of the program, and \textit{derived relations} that are defined from the basic relations and events in the weak memory model specification. Constraints over relations that are specified by weak memory models are defined as requirements of acyclicity, irreflexivity or emptiness of specific relations~\cite{alglave2016syntax}.

@@

    \item The \textit{data-flow} of a program is defined by \textit{communication relations}:
    \begin{itemize}[noitemsep]
        \item the \textit{read-from} relation \rf{}~$\subseteq~\mathbb{W}~\times~\mathbb{R}$ that maps each write event to the read event that reads the value written by write event; and
        \item the \textit{coherence order} relation \co{}~$\subseteq~\mathbb{W}~\times~\mathbb{W}$ that defines the total order on writes to the same location across all processes (also called the \textit{write serialisation}, \texttt{ws}-relation).
    \end{itemize}

>>>>

The relation~$r\,\subseteq~\mathbb{E}~\times~\mathbb{E}$ is a set of pairs of events (a subset of Cartesian product of two sets of events). There are two kinds of relations between events: \textit{basic relations} that capture the semantics of the program, and \textit{derived relations} that are defined from the basic relations and events in the weak memory model specification. Constraints over relations that are specified by weak memory models are defined as requirements of \textit{acyclicity}, \textit{irreflexivity} or \textit{emptiness} of specific relations~\cite{alglave2016syntax}.

@@

    \item The \textit{data-flow} of a program is defined by \textit{communication relations}:
    \begin{itemize}[noitemsep]
        \item the \textit{read-from} relation \rf{}~$\subseteq~\mathbb{W}~\times~\mathbb{R}$ that maps each write event to the read event that reads the value written by write event; and
        \item the \textit{coherence-order} relation \co{}~$\subseteq~\mathbb{W}~\times~\mathbb{W}$ that defines the total order on writes to the same location across all processes (also called the \textit{write serialisation}, \texttt{ws}-relation).
    \end{itemize}

### 2018-05-20 3_encod.tex
Add some comments to the paper.

\begin{definition}[Portability]
Let $\mathcal{M_S}$, $\mathcal{M_T}$ be two weak memory models. A program $P$ is portable from $\mathcal{M_S}$ to $\mathcal{M_T}$ if 
$\textit{cons}_{\mathcal{M_T}}(P) \subseteq \textit{cons}_{\mathcal{M_S}}(P)$
\end{definition}

@@

The control-flow of a program is represented by the \textit{control-flow graph}, a directed acyclic connected graph with a single source and multiple sink nodes. %TODO: footnote why multiple sinks
In a control-flow graph, there are two types of edges (transitions): \textit{primary transitions} that denote unconditional jumps or if-true-transitions (pictured with solid lines), and \textit{alternative transitions} that denote if-false-transitions (pictured with dotted lines).
Each node on graph can have either one successor (primary) or two successors (both primary and alternative); only computation events can serve as a branching point).
However, each merge node can have any positive number of predecessors, where each edge may be either primary or alternative.

@@

All control-flow edges contain a label that denotes the \textit{guard}, a predicate that determines the transition.
An empty guard (a \textit{true} predicate) is denoted as $\epsilon$.
A guard depends on the data-flow of the program, it represents a memory unit or a computational expression that is liable to the weak memory model relaxations.
The branching expressions that support more than two outgoing control-flow edges may be useful for describing non-deterministic transition systems, where the guards are not necessarily mutually exclusive.
However, as the C language supports only binary logic (\textit{if-then-else} branching), \porthos[2] builds only two possible outcomes of evaluating a guard (\textit{primary} and \textit{alternative} transition), see Section~\ref{ch:impl:model:xgraph:edges} for details.

@@

@@

Following~\cite{Porthos17b}, the indexed references of variables are computed in accordance with the following rules:
%\begin{enumerate}[noitemsep,topsep=0pt]
(1)~any access to a shared variable (both read and write) increments its SSA-index;
(2)~only writes to a local variable increment its SSA-index (reads preserve indices);
(3)~no access to a constant variable or computed (evaluated) expression changes their %SSA-index.
%\end{enumerate}
These rules determine the following encoding of load, store and computation events within single thread:
%TODO: maybe add the overall formula \phi_{DF} ?
%
\begin{align}
    \phi_{DF_{e = \texttt{load}(r \leftarrow l)}}  \defeq \ & [\fx(e) \Rightarrow (r_{i+1} = l_{i+1})] \\
    \phi_{DF_{e = \texttt{store}(l \leftarrow r)}} \defeq \ & [\fx(e) \Rightarrow (l_{i+1} = r_i)] \\
    \phi_{DF_{e = \texttt{eval}(\cdot)}}           \defeq \ & [\fx(e) \Rightarrow \fv(e)] % \\
\end{align}

>>>>

\begin{definition}[Portability]
Let $\mathcal{M_S}$, $\mathcal{M_T}$ be two weak memory models.
The program $P$ is portable from $\mathcal{M_S}$ to $\mathcal{M_T}$ if 
$\textit{cons}_{\mathcal{M_T}}(P) \subseteq \textit{cons}_{\mathcal{M_S}}(P)$
\end{definition}

@@

The control-flow of a program is represented by the \textit{control-flow graph}, a directed acyclic connected graph with a single source and multiple sink nodes. %TODO: footnote why multiple sinks
The edges of 
%In a control-flow graph, there are two types of edges (transitions): \textit{primary transitions} that denote unconditional jumps or if-true-transitions (pictured with solid lines), and \textit{alternative transitions} that denote if-false-transitions (pictured with dotted lines).
All control-flow edges contain a label that denotes the \textit{guard}, a predicate that determines the transition.
An empty guard (a \textit{true} predicate) is denoted as $\epsilon$.
A guard depends on the data-flow of the program, it represents a memory unit or a computational expression that is liable to the weak memory model relaxations.
The branching expressions that support more than two outgoing control-flow edges may be useful for describing non-deterministic transition systems, where the guards are not necessarily mutually exclusive.
However, as the C language supports only binary logic (\textit{if-then-else} branching), \porthos[2] builds only two possible outcomes of evaluating a guard (\textit{primary} and \textit{alternative} transition), see Section~\ref{ch:impl:model:xgraph:edges} for details.
%Each node on graph can have either one successor (primary) or two successors (both primary and alternative); only computation events can serve as a branching point).
%However, each merge node can have any positive number of predecessors, where each edge may be either primary or alternative.

@@

@@

\textbf{TODOOOOOOOOOOOOOOOOOOOOOOOOOOOO!!!!!!!!!!!!!!!!!!!!!!! NOPS IN THIS PICTURE!!!!}

@@

Following~\cite{Porthos17b}, the indexed references of variables are computed in accordance with the following rules:
(1)~any access to a shared variable (both read and write) increments its SSA-index;
(2)~only writes to a local variable increment its SSA-index (reads preserve indices);
(3)~no access to a constant variable or computed (evaluated) expression changes their SSA-index.
These rules determine the following encoding of load, store and computation events within single thread:
%TODO: maybe add the overall formula \phi_{DF} ?
%
\begin{align}
    \phi_{DF_{e = \texttt{load}(r \leftarrow l)}}  \defeq \ & [\fx(e) \Rightarrow (r_{i+1} = l_{i+1})] \\
    \phi_{DF_{e = \texttt{store}(l \leftarrow r)}} \defeq \ & [\fx(e) \Rightarrow (l_{i+1} = r_i)] \\
    \phi_{DF_{e = \texttt{eval}(\cdot)}}           \defeq \ & [\fx(e) \Rightarrow \fv(e)] % \\
\end{align}
